Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/introduction.tex
Deleted smth in intro/related work/econ.

Whether data gives competitive advantage
has been studied theoretically in \cite{varian2018artificial,
  lambrecht2015can} and empirically in
\cite{bajari2018impact}.
While these papers find that small amounts
  of additional data do not provide significant improvement,
 % in training a more predictive model,
  they focus on learning in isolation.
  %, which overlooks certain aspects in a competition.
%\swdelete{These studies consider the effect of additional data in terms of helping towards solving a machine learning problem in isolation and argue that it does not play a large role.}
We ask how additional data helps when firms simultaneously solve a machine learning problem and compete for consumers. Due to the competition dynamics in our model, we find that even a small amount of additional data tends to help a lot. The first-mover advantage has been well-studied in other settings in economics and marketing, see survey \cite{kerin1992first}.

>>>>

Whether data gives competitive advantage
has been studied theoretically in \cite{varian2018artificial,
  lambrecht2015can} and empirically in
\cite{bajari2018impact}.
While these papers find that small amounts
  of additional data do not provide significant improvement,
 % in training a more predictive model,
  they focus on learning in isolation.
  %, which overlooks certain aspects in a competition.
%\swdelete{These studies consider the effect of additional data in terms of helping towards solving a machine learning problem in isolation and argue that it does not play a large role.}
\asdelete{We ask how additional data helps when firms simultaneously solve a machine learning problem and compete for consumers. Due to the competition dynamics in our model, we find that even a small amount of additional data tends to help a lot.}
The first-mover advantage has been well-studied in other settings in economics and marketing, see survey \cite{kerin1992first}.
